---
title: "Curation of Bioconductor package metadata, targeting EDAM ontology and ELIXIR bio.tools metadata schemas"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Curation of Bioconductor package metadata, targeting EDAM ontology and ELIXIR bio.tools metadata schemas}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

This vignette is derived almost entirely from collaborative
code supplied by Anh Nguyet Vu of Sage Bionetworks.  The purpose
is to illustrate usage of OpenAPI transformation to
provide systematic organization and tagging of content
available for Bioconductor packages.

# Example 1: chromVAR

```{r doone, message=FALSE}
library(biocEDAM)
library(listviewer)
library(reticulate)
docv = curate_bioc()
```
The curation step uses an OpenAI API key.
The curated view of the chromVAR landing page
at bioconductor.org is:

```{r lookbase}
jsonedit(py_to_r(docv[[1]]))
```

The README of the chromVAR github repo provides
additional metadata.

```{r lkdev}
jsonedit(py_to_r(docv[[2]]))
```

These can be "merged" for a richer metadata artifact.

# Example 2: DESeq2

```{r lknxt}
dotx = curate_bioc(
 "tximport", 
 devurl = "https://raw.githubusercontent.com/thelovelab/tximport/refs/heads/devel/vignettes/tximport.Rmd")
full = c(py_to_r(dotx[[1]]), py_to_r(dotx[[2]]))
jsonedit(full)
```
